Comparison of Log Likelihood Values

### 2017-10-30 R/LogLikelihood_Comparison.Rmd
Updated log likelihood values after changing the parks dataset by removing private parks and sports stadiums.

### Boston SEM Models
Models 3 and 6 are most likely for all three dependent variables.
```{r boston_SEM_models, echo=FALSE}

@@

### Boston SDM Models
Models 1 and 3 are most likely for all three dependent variables.
```{r boston_SDM_models, echo=FALSE}

@@

NYC_SEM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SEM_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
NYC_SEM_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
NYC_SEM_Loglikelihoods[,3] <- c(-2716.36, -2716.36, -2716.36)
NYC_SEM_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
NYC_SEM_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
NYC_SEM_Loglikelihoods[,6] <- c(-2716.33, -2716.33, -2716.33)
colnames(NYC_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

@@

NYC_SDM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SDM_Loglikelihoods[,1] <- c(-3819.95, -3819.95, -3819.95)
NYC_SDM_Loglikelihoods[,2] <- c(-4369.45, -4369.45, -4369.45)
NYC_SDM_Loglikelihoods[,3] <- c(-2656.60, -2656.60, -2656.60)
NYC_SDM_Loglikelihoods[,4] <- c(-3808.52, -3808.53, -3812.65)
NYC_SDM_Loglikelihoods[,5] <- c(-4368.97, -4368.96, -4368.45)
NYC_SDM_Loglikelihoods[,6] <- c(-2655.48, -2655.48, -2655.36)
colnames(NYC_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

>>>>

### Boston SEM Models
Models 3 and 6 are most likely for all three dependent variables. (**These log likelihood values are not up to date but I am holding off on updating them because the park access coeffficient is not significant in any of the models**)
```{r boston_SEM_models, echo=FALSE}

@@

### Boston SDM Models
Models 1 and 3 are most likely for all three dependent variables. (**These log likelihood values are not up to date but I am holding off on updating them because the park access coeffficient is not significant in any of the models**)
```{r boston_SDM_models, echo=FALSE}

@@

NYC_SEM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SEM_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
NYC_SEM_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
NYC_SEM_Loglikelihoods[,3] <- c(-2716.36, -2716.36, -2716.36)
NYC_SEM_Loglikelihoods[,4] <- c(-3929.15, -3929.15, -3929.38)
NYC_SEM_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
NYC_SEM_Loglikelihoods[,6] <- c(-2716.33, -2716.33, -2716.33)
colnames(NYC_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

@@

NYC_SDM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SDM_Loglikelihoods[,1] <- c(-3819.95, -3819.95, -3819.95)
NYC_SDM_Loglikelihoods[,2] <- c(-4369.45, -4369.45, -4369.45)
NYC_SDM_Loglikelihoods[,3] <- c(-2656.60, -2656.60, -2656.60)
NYC_SDM_Loglikelihoods[,4] <- c(-3808.43, -3808.44, -3812.56)
NYC_SDM_Loglikelihoods[,5] <- c(-4368.96, -4368.96, -4368.43)
NYC_SDM_Loglikelihoods[,6] <- c(-2655.48, -2655.48, -2655.36)
colnames(NYC_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
